Topological Equivariant Artist Model

### 2022-01-26 slides/main.tex
openset gamma notation

    \frametitle<3|handout:3>{Functor: $\vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}$}

@@

            \onslide*<0|handout:2,3,5>{\sheafc_{\gbasec, \gtotalc}} 

@@

            \onslide*<0|handout:5>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}  

@@

            \onslide*<0|handout:2->{\gbasec}

@@

            \onslide*<0|handout:4>{\arrow[d, dashed, maps to, color=sheaf]} \&  \& 
            \onslide*<0|handout:1,3->{\dbasec}

@@

            \onslide*<0|handout:5>{\arrow[u, dashed, maps to, color=sheaf]} \\
            \onslide*<0|handout:4>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}} 

@@

            \onslide*<0|handout:1,3-4>{\sheafc_{\dbasec, \dtotalc}}

>>>>

    \frametitle<3|handout:3>{Functor: $\vindexc: \opensetgc \rightarrow \opensetc$}

@@

            \onslide*<0|handout:2,3,5>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 

@@

            \onslide*<0|handout:5>{\cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}}}  

@@

            \onslide*<0|handout:2->{\opensetgc}

@@

            \onslide*<0|handout:4>{\arrow[d, dashed, maps to, "\sheaf_{\gbasec, \vindexpullc\dtotalc}"',color=sheaf]} \&  \& 
            \onslide*<0|handout:1,3->{\opensetc}

@@

            \onslide*<0|handout:5>{\arrow[u, dashed, maps to, "\sheaf_{\dbasec, \vindexpushc\gtotalc}"', color=sheaf]} \\
            \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}} 

@@

            \onslide*<0|handout:1,3-4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
